### 2015-03-02 docs/Paper/paper.tex
Paper in progress, just needs good data

\documentclass[11pt]{article}
\title{Geant4 Benchmark Analysis: Al cube and He cylindrical chamber}
\author{Shaun Marshall}
\date{\today}
\usepackage{abstract}
\usepackage{multicol}
\usepackage{anysize}
\usepackage{graphicx}
\usepackage{float}

% Figures within a column...
\makeatletter
\newenvironment{tablehere}
{\def\@captype{table}}
{}
\newenvironment{figurehere}
{\def\@captype{figure}}
{}
\makeatother

\marginsize{1 in}{1 in}{1 in}{1 in}
\begin{document}
\maketitle

\begin{abstract}\emph{
This experiment analyzes a setup of interest, firing collimated protons at varying decades of energy at an aluminum box 50 cm away of side 5, 10, and 25 cm, 50 cm in front of a cylindrical container of helium.  The analytical tasks with which to assess and characterize the scenario include an energy deposition map, charge displacemnent map, and particle creation probabilities tables.  Results are comparable to empirical studies of proton dosimetry and demonstrate sensitivity of Geant4.
}\end{abstract}

\begin{multicols}{2}

\section{Introduction}

\section{Procedure}

Collimated protons were fired at the Al block from 50 cm away, which lie in front of a cylindrical He gas chamber centered in line with the block vertically, perpendicular to the cylinder's long axis; the solid geometry lie in a vacuum (fig~\ref{fig:schematic}).  This geometry was adjusted and retested for the 5, 10 and 25 cm side lengths  of the Al.  Energy deposition and net charge transfer by millimeter is recorded and normalized per primary proton.  Proton and neutron production combitions are found in time with gamma ray creation.  The resulting data were plotted with Gnuplot.

\begin{figurehere}
\centering
\resizebox{\columnwidth}{!}{\includegraphics{../testrun.png}}
\caption{\label{fig:schematic}\small \emph{Schematic of constructed detector geometry with sample event}}
\end{figurehere}

\section{Discussion}

\section{Conclusion}

\end{multicols}
\end{document}

### 2015-03-02 src/src/RunAction.cc

@@ -150,12 +150,6 @@ void RunAction::EndOfRunAction(const G4Run* run) {
   fileNameStream << data_dir << data_dir_geo << Al_side << "/" << data_dir_energy << E_Num << "/bins.dat";
   fileName = fileNameStream.str();
 
-  // Remove previous worker file
-  G4String rmBins;
-  std::ifstream binsFileStreamTest;
-  binsFileStreamTest.open(fileName);
-  if ( binsFileStreamTest.good() ) { rmBins = "rm " + fileName; system(rmBins); }
-
   fileStream.open (fileName, std::ios::app);
   fileStream << "#  z (mm)   Energy_Dep  Net_Charge\n";
   for ( G4int binNum = 0; binNum<numBins; binNum++ ) {
@@ -166,12 +160,6 @@ void RunAction::EndOfRunAction(const G4Run* run) {
   fileNameStream.str(""); fileName = "";
   fileNameStream << data_dir << data_dir_geo << Al_side << "/" << data_dir_energy << E_Num << "/production.dat";
   fileName = fileNameStream.str();
-
-  // Remove previous worker file
-  G4String rmProduction;
-  std::ifstream prodFileStreamTest;
-  prodFileStreamTest.open(fileName);
-  if ( prodFileStreamTest.good() ) { rmProduction = "rm " + fileName; system(rmProduction); }
 
   // Add content
   fileStream.open (fileName, std::ios::app);
@@ -192,12 +180,6 @@ void RunAction::EndOfRunAction(const G4Run* run) {
   G4String gnuFileName;
   gnuFileNameStream << data_dir << data_dir_geo << Al_side << "/" << data_dir_energy << E_Num << "/graphs.gplot";
   gnuFileName = gnuFileNameStream.str();
-
-  // Remove previous worker file
-  G4String rmGnu;
-  std::ifstream gnuFileStreamTest;
-  gnuFileStreamTest.open(gnuFileName);
-  if ( gnuFileStreamTest.good() ) { rmGnu = "rm " + gnuFileName; system(rmGnu); }
 
   // Add content
   gnuFileStream.open (gnuFileName, std::ios::app);

### 2015-03-02 src/src/RunAction.cc
Fixed auto gnuplot figure generation and math errors

@@ -5,6 +5,7 @@
 #include "G4RunManager.hh"
 #include "G4UnitsTable.hh"
 #include "G4SystemOfUnits.hh"
+#include "G4Threading.hh"
 
 #include <iostream>
 #include <fstream>
@@ -17,32 +18,35 @@ RunAction::RunAction() : G4UserRunAction() {}
 RunAction::~RunAction() { delete G4AnalysisManager::Instance(); }
 
 void RunAction::BeginOfRunAction(const G4Run* run) {
-  // Directory info
-  G4String fileVarGet;
-  G4String data_dir = "data/";
+  // Primary thread
+  if ( G4Threading::G4GetThreadId() == 0 ) {
+    // Directory info
+    G4String fileVarGet;
+    G4String data_dir = "data/";
 
-  // I/O vars
-  std::ostringstream fileNameStream;
-  std::ofstream fileStream;
-  G4String fileName;
+    // I/O vars
+    std::ostringstream fileNameStream;
+    std::ofstream fileStream;
+    G4String fileName;
 
-  // Acqiure state vars
-  G4int Al_side;
-  fileNameStream.str(""); fileName = "";
-  fileNameStream << data_dir << ".state";
-  fileName = fileNameStream.str();
-  std::ifstream stateFile;
-  stateFile.open(fileName);
-  stateFile >> fileVarGet;
-  Al_side = atoi(fileVarGet);
+    // Acqiure state vars
+    G4int Al_side;
+    fileNameStream.str(""); fileName = "";
+    fileNameStream << data_dir << ".state";
+    fileName = fileNameStream.str();
+    std::ifstream stateFile;
+    stateFile.open(fileName);
+    stateFile >> fileVarGet;
+    Al_side = atoi(fileVarGet);
 
-  // Primary energy (run) number and total events
-  G4int E_Num = run->GetRunID();
-  // Adjust Energy number by state var
-  G4int Al_num = 0;   if ( Al_side == 10 ) Al_num = 1; if ( Al_side == 25 ) Al_num = 2;
-  E_Num = E_Num - Al_num*45 + 1;
+    // Primary energy (run) number and total events
+    G4int E_Num = run->GetRunID();
+    // Adjust Energy number by state var
+    G4int Al_num = 0;   if ( Al_side == 10 ) Al_num = 1; if ( Al_side == 25 ) Al_num = 2;
+    E_Num = E_Num - Al_num*45 + 1;
 
[…]

### 2015-03-03 src/cube-to-cyl.cc
Nicer gnuplot output, adding neutrons to macro, working out kinks in event identification

@@ -108,6 +108,7 @@ int main(int argc,char** argv) {
 	std::ostringstream dirCommandStream;
 	G4String data_dir = "data/";
 	G4String data_dir_geo = "Al";
+	G4String data_dir_particle = "p";
 	G4String data_dir_energy = "E";
 	G4String data_dir_analysis = "Analysis";
 	// Make base dir
@@ -121,19 +122,23 @@ int main(int argc,char** argv) {
 	  dirCommand = dirCommandStream.str();
       system(dirCommand);
       
-      for (G4int E_num=1; E_num<=45; E_num++) {
-        // Energy dir iteration
-        dirCommandStream.str(""); dirCommand = "";
-        dirCommandStream << "mkdir -p " << data_dir << data_dir_geo << Al_side[al_num] << "/" << data_dir_energy << E_num << "/";
-	    dirCommand = dirCommandStream.str();
-        system(dirCommand);
-        
-        for (G4int analysis_num=1; analysis_num<=3; analysis_num++) {
-          // Analysis dir iteration
+      for (G4int particle_num=1; particle_num<=2; particle_num++) {
+		if ( particle_num == 2) { data_dir_particle = "n"; }
+		  
+        for (G4int E_num=1; E_num<=45; E_num++) {
+          // Energy dir iteration
           dirCommandStream.str(""); dirCommand = "";
-          dirCommandStream << "mkdir -p " << data_dir << data_dir_geo << Al_side[al_num] << "/" << data_dir_energy << E_num << "/" << data_dir_analysis << analysis_num << "/";
+          dirCommandStream << "mkdir -p " << data_dir << data_dir_geo << Al_side[al_num] << "/" << data_dir_particle << data_dir_energy << E_num << "/";
 	      dirCommand = dirCommandStream.str();
           system(dirCommand);
+        
+          for (G4int analysis_num=1; analysis_num<=3; analysis_num++) {
+            // Analysis dir iteration
+            dirCommandStream.str(""); dirCommand = "";
+            dirCommandStream << "mkdir -p " << data_dir << data_dir_geo << Al_side[al_num] << "/" << data_dir_particle << data_dir_energy << E_num << "/" << data_dir_analysis << analysis_num << "/";
+	        dirCommand = dirCommandStream.str();
+            system(dirCommand);
+          }
         }
       }
 	}

### 2015-03-03 src/src/EventAction.cc

@@ -48,6 +48,7 @@ void EventAction::EndOfEventAction(const G4Event* event) {
   G4String fileVarGet;
   G4String data_dir = "data/";
   G4String data_dir_geo = "Al";
+  G4String data_dir_particle = "p";
   G4String data_dir_energy = "E";
   G4String data_dir_analysis = "Analysis";
   
@@ -64,9 +65,10 @@ void EventAction::EndOfEventAction(const G4Event* event) {
   // Primary energy (run) number and event number
   G4int E_Num = G4RunManager::GetRunManager()->GetCurrentRun()->GetRunID();
   G4int eventNum = event->GetEventID();
-  // Adjust Energy number by state var
+  // Adjust Energy number by state var, beam particle by energy number
   G4int Al_num = 0;   if ( Al_side == 10 ) Al_num = 1; if ( Al_side == 25 ) Al_num = 2;
-  E_Num = E_Num - Al_num*45 + 1;
+  E_Num = E_Num - Al_num*90 + 1;
+  if ( E_Num > 45 ) { E_Num = E_Num - 45; data_dir_particle = "n"; }
 
   // Invoke stat vars  
   G4int zBin;
@@ -75,11 +77,11 @@ void EventAction::EndOfEventAction(const G4Event* event) {
   G4String particleLocation, particleName;
   
   // Bin and tally files
-  energyFileNameStream << data_dir << data_dir_geo << Al_side << "/" << data_dir_energy << E_Num << "/energy.txt";
+  energyFileNameStream << data_dir << data_dir_geo << Al_side << "/" << data_dir_particle << data_dir_energy << E_Num << "/energy.txt";
   energyFileName = energyFileNameStream.str();
   std::ofstream energyFile;
   energyFile.open(energyFileName, std::ios::app);
-  chargeFileNameStream << data_dir << data_dir_geo << Al_side << "/" << data_dir_energy << E_Num << "/charge.txt";
+  chargeFileNameStream << data_dir << data_dir_geo << Al_side << "/" << data_dir_particle << data_dir_energy << E_Num << "/charge.txt";
   chargeFileName = chargeFileNameStream.str();
   std::ofstream chargeFile;
   chargeFile.open(chargeFileName, std::ios::app);
@@ -87,7 +89,7 @@ void EventAction::EndOfEventAction(const G4Event* event) {
   
   // 1 Energy Deposition
   fileNameStream.str(""); fileName = "";
[…]

### 2015-03-03 src/src/RunAction.cc

@@ -13,6 +13,7 @@
 #include <stdio.h>
 #include <unistd.h>
 #include <sys/types.h>
+#include <algorithm>
 
 RunAction::RunAction() : G4UserRunAction() {}
 RunAction::~RunAction() { delete G4AnalysisManager::Instance(); }
@@ -23,6 +24,7 @@ void RunAction::BeginOfRunAction(const G4Run* run) {
     // Directory info
     G4String fileVarGet;
     G4String data_dir = "data/";
+    G4String data_dir_particle = "p";
 
     // I/O vars
     std::ostringstream fileNameStream;
@@ -41,11 +43,12 @@ void RunAction::BeginOfRunAction(const G4Run* run) {
 
     // Primary energy (run) number and total events
     G4int E_Num = run->GetRunID();
-    // Adjust Energy number by state var
+    // Adjust Energy number by state var, beam particle by energy number
     G4int Al_num = 0;   if ( Al_side == 10 ) Al_num = 1; if ( Al_side == 25 ) Al_num = 2;
-    E_Num = E_Num - Al_num*45 + 1;
+    E_Num = E_Num - Al_num*90 + 1;
+    if ( E_Num > 45 ) { E_Num = E_Num - 45; data_dir_particle = "n"; }
 
-    G4cout << "Running energy " << E_Num << " for Al=" << Al_side << G4endl;
+    G4cout << "Running " << data_dir_particle << " energy #" << E_Num << " for Al=" << Al_side << G4endl;
   }
 }
 
@@ -75,6 +78,7 @@ void RunAction::EndOfRunAction(const G4Run* run) {
   G4String fileVarGet;
   G4String data_dir = "data/";
   G4String data_dir_geo = "Al";
+  G4String data_dir_particle = "p";
   G4String data_dir_energy = "E";
   G4String data_dir_analysis = "Analysis";
   
@@ -91,9 +95,10 @@ void RunAction::EndOfRunAction(const G4Run* run) {
   // Primary energy (run) number and total events
   G4int E_Num = run->GetRunID();
   G4int numEvents = run->GetNumberOfEventToBeProcessed();
-  // Adjust Energy number by state var
+  // Adjust Energy number by state var, beam particle by energy number
   G4int Al_num = 0;   if ( Al_side == 10 ) Al_num = 1; if ( Al_side == 25 ) Al_num = 2;
[…]

### 2015-03-03 src/src/SteppingAction.cc

@@ -49,6 +49,7 @@ void SteppingAction::UserSteppingAction(const G4Step* step) {
   G4String fileVarGet;
   G4String data_dir = "data/";
   G4String data_dir_geo = "Al";
+  G4String data_dir_particle = "p";
   G4String data_dir_energy = "E";
   G4String data_dir_analysis = "Analysis";
   
@@ -64,9 +65,10 @@ void SteppingAction::UserSteppingAction(const G4Step* step) {
   // Primary event number and energy (run) number
   G4int eventNum = G4RunManager::GetRunManager()->GetCurrentEvent()->GetEventID();
   G4int E_Num = G4RunManager::GetRunManager()->GetCurrentRun()->GetRunID();
-  // Adjust Energy number by state var
+  // Adjust Energy number by state var, beam particle by energy number
   G4int Al_num = 0;   if ( Al_side == 10 ) Al_num = 1; if ( Al_side == 25 ) Al_num = 2;
-  E_Num = E_Num - Al_num*45 + 1;
+  E_Num = E_Num - Al_num*90 + 1;
+  if ( E_Num > 45 ) { E_Num = E_Num - 45; data_dir_particle = "n"; }
   
   // Get half-length of world to fix z counting [(-L/2, L/2) -> (0, L)]
   G4double worldZHalfLength = 0; G4Box* worldBox = 0;
@@ -87,7 +89,7 @@ void SteppingAction::UserSteppingAction(const G4Step* step) {
   G4double particleEDep = step->GetTotalEnergyDeposit();
   // + final bin
   fileNameStream.str(""); fileName = "";
-  fileNameStream << data_dir << data_dir_geo << Al_side << "/" << data_dir_energy << E_Num << "/" << data_dir_analysis << "1/event" << eventNum << ".txt";
+  fileNameStream << data_dir << data_dir_geo << Al_side << "/" << data_dir_particle << data_dir_energy << E_Num << "/" << data_dir_analysis << "1/event" << eventNum << ".txt";
   fileName = fileNameStream.str();
   fileStream.open (fileName, std::ios::app);
   fileStream << zBin_final << " " << particleEDep << "\n";
@@ -104,7 +106,7 @@ void SteppingAction::UserSteppingAction(const G4Step* step) {
     if ( particleCharge != 0 ) {
       // - init bin
       fileNameStream.str(""); fileName = "";
[…]

### 2015-03-03 src/cube-to-cyl.cc
Event errors removed, was not creating p dirs after n dirs; neutron data produced

@@ -96,44 +96,47 @@ int main(int argc,char** argv) {
 
   // batch mode  
   if ( macro.size() ) {
-	// 10 micrometer particle track cuts
+    // 10 micrometer particle track cuts
     G4String cutCommand = "/run/setCut 0.01 mm";
     UImanager->ApplyCommand(cutCommand);
     
     // Experimental Parameters
-	G4int Al_side[3] = {5, 10, 25};
+    G4int Al_side[3] = {5, 10, 25};
 	
-	// Create data analysis directory tree
-	G4cout << "Creating data analysis tree..." << G4endl;
-	std::ostringstream dirCommandStream;
-	G4String data_dir = "data/";
-	G4String data_dir_geo = "Al";
-	G4String data_dir_particle = "p";
-	G4String data_dir_energy = "E";
-	G4String data_dir_analysis = "Analysis";
-	// Make base dir
-	dirCommandStream << "mkdir -p " << data_dir;
-	G4String dirCommand = dirCommandStream.str();
+    // Create data analysis directory tree
+    G4cout << "Creating data analysis tree..." << G4endl;
+    std::ostringstream dirCommandStream;
+    G4String data_dir = "data/";
+    G4String data_dir_geo = "Al";
+    G4String data_dir_particle = "p";
+    G4String data_dir_energy = "E";
+    G4String data_dir_analysis = "Analysis";
+
+    // Make base dir
+    dirCommandStream << "mkdir -p " << data_dir;
+    G4String dirCommand = dirCommandStream.str();
     system(dirCommand);
+
+    // Geometry dir iteration
     for (G4int al_num=0; al_num<3; al_num++) {
-	  // Geometry dir iteration
-	  dirCommandStream.str(""); dirCommand = "";
+      dirCommandStream.str(""); dirCommand = "";
       dirCommandStream << "mkdir -p " << data_dir << data_dir_geo << Al_side[al_num] << "/";
-	  dirCommand = dirCommandStream.str();
+      dirCommand = dirCommandStream.str();
       system(dirCommand);
       
-      for (G4int particle_num=1; particle_num<=2; particle_num++) {
-		if ( particle_num == 2) { data_dir_particle = "n"; }
+      // p,nE#/ dir iteration
+      for ( G4int particle_num=1; particle_num<=2; particle_num++ ) {
+        if ( particle_num == 1 ) { data_dir_particle = "p"; }
[…]

### 2015-03-03 src/src/RunAction.cc

@@ -198,10 +198,10 @@ void RunAction::EndOfRunAction(const G4Run* run) {
     G4int E_Int = (E_Num % 5); if ( E_Int == 0 ) { E_Int = 5; }
     std::ostringstream energy_stringStream;
     energy_stringStream << E_Int;
-    if ( E_Num % 15 > 5 ) { energy_stringStream << "0"; }
-    if ( E_Num % 15 > 10 ) { energy_stringStream << "0"; }
+    if ( (( E_Num % 15 ) > 5) || (( E_Num % 15) == 0) ) { energy_stringStream << "0"; }
+    if ( (( E_Num % 15 ) > 10) || (( E_Num % 15) == 0) ) { energy_stringStream << "0"; }
     if ( ( 15 < E_Num ) && ( E_Num < 31 ) ) { energy_stringStream << " k"; }
-    if ( ( E_Num > 30 ) && ( E_Num < 46) ) { energy_stringStream << " Me"; }
+    if ( ( E_Num > 30 ) && ( E_Num < 46) ) { energy_stringStream << " M"; }
     energy_stringStream << "eV";
     if ( data_dir_particle == "p" ) { energy_stringStream << " Protons"; }
     if ( data_dir_particle == "n" ) { energy_stringStream << " Neutrons"; }
@@ -212,15 +212,15 @@ void RunAction::EndOfRunAction(const G4Run* run) {
     gnuFileStream << "set term png\n" << \
                      "set output \"fig_EDep.png\"\n" << \
                      "set key samplen 2 spacing 0.9 font \",8\" below\n" << \
-                     "set title \"Energy Deposition per " << energy_string << "\n" << \
+                     "set title \"Net Energy Deposition per " << energy_string << "\n" << \
                      "set xlabel \"Position (mm)\"\n" << \
-                     "set ylabel \"dE/dx (eV/[mm * p+])\"\n" << \
+                     "set ylabel \"Energy (eV/" << data_dir_particle << ")\"\n" << \
                      "plot \"bins.dat\" u 1:2 t \"Energy_Dep\"\n" << \
                      "set output \"fig_ChargeDep.png\"\n" << \
                      "set key samplen 2 spacing 0.9 font \",8\" below\n" << \
                      "set title \"Net Charge per " << energy_string << "\n" << \
                      "set xlabel \"Position (mm)\"\n" << \
-                     "set ylabel \"dQ/dx (e/[mm * p+])\"\n" << \
[…]

### 2015-03-08 docs/Paper/paper.tex
Fixed gnuplottable (final thread) output, added procedures to paper

@@
 \usepackage{graphicx}
+\usepackage{url}
 \usepackage{float}
@@
 \newenvironment{tablehere}
-{\def\@captype{table}}
-{}
+{\def\@captype{table}}{}
 \newenvironment{figurehere}
-{\def\@captype{figure}}
-{}
+{\def\@captype{figure}}{}
 \makeatother
 
-\marginsize{1 in}{1 in}{1 in}{1 in}
+\marginsize{0.75 in}{0.75 in}{0.75 in}{0.75 in}
 \begin{document}
@@
 \begin{abstract}\emph{
-This experiment analyzes a setup of interest, firing collimated protons at varying decades of energy at an aluminum box 50 cm away of side 5, 10, and 25 cm, 50 cm in front of a cylindrical container of helium.
+This experiment analyzes a setup of interest, firing collimated protons and neutrons in the range of $10^0-5\cdot10^8\ eV$ at an aluminum box 50 cm away of side 5, 10, and 25 cm, 50 cm, in front of a cylindrical container of helium 50 cm further.
 The analytical tasks with which to assess and characterize the scenario include an energy deposition map, charge displacemnent map, and particle creation probabilities tables.
-Results are comparable to empirical studies of proton dosimetry and demonstrate sensitivity of Geant4.
+Results are comparable to empirical studies of proton dosimetry and demonstrate validity of Geant4 theoretical modeling.
 }\end{abstract}
@@
 
-Collimated protons were fired at the Al block from 50 cm away, which lie in front of a cylindrical He gas chamber centered in line with the block vertically, perpendicular to the cylinder's long axis; the solid geometry lie in a vacuum (fig~\ref{fig:schematic}).
-This geometry was adjusted and retested for the 5, 10 and 25 cm side lengths  of the Al.
-Energy deposition and net charge transfer by millimeter is recorded and normalized per primary proton.
-Proton and neutron production combitions are found in time with gamma ray creation.
-The resulting data were plotted with Gnuplot.
+1 million simulated events of collimated protons and neutrons were fired 50 cm to an Aluminum block in a vacuous world, which lie 50 cm in front of a cylindrical He gas chamber centered in line with the block vertically, perpendicular to the cylinder's long axis (fig~\ref{fig:schematic}).
+This geometry was iterated for the 5, 10 and 25 cm side lengths of the block.
+Energy deposition and net charge transfer by millimeter were recorded and normalized per primary.
+Proton and neutron production combinations are found in time with gamma ray creation.
 
@@
 \resizebox{\columnwidth}{!}{\includegraphics{../testrun.png}}
-\caption{\label{fig:schematic}\small \emph{Schematic of constructed detector geometry with sample event}}
+\caption{\label{fig:schematic}\small \emph{Schematic of constructed detector geometry with sample event, using Geant4 OpenGL visualization.}}
 \end{figurehere}
+
+The FTFP\_BERT physics list was utilized\cite{Geant4:physicsList}, with track cuts at a 10 micron minimum step legnth.
+Primary particle energies range from $1$ to $5\cdot10^x$, where $x:\mathcal{Z}\in[0,8]$.
+
+\subsection{Energy Deposition Tracking}
+
+To acquire an energy deposition map of proton and neutron events in this physical setup, a script was introduced into the UserSteppingAction class.
+This script acquired the position (in mm) and energy (in MeV) of every collision (G4Step) per event.
+A UserRunAction method took averages ofenergy depositions throughout the 1150 mm world per bin, event, primary energy (G4Run) and geometry.
+
+\subsection{Charge Deposition Tracking}
+
+The charge deposition map for the proton and neutron events also utilized a UserSteppingAction script to obtain spatial values of charge displacement.
+Dividing the world into (mm) bins, charge values of particles which gained momentum per event are subtracted from the bin of track vertex and added to the bin of track end.
+The end of each G4Run included an averaging of the net charge per bin, event, energy and geometry; this net charge signature depicts the average polarization of the detectors.
+
+\subsection{Particle Production Tracking}
+
+Probably particle production matrices $P(n,m)$ were constructed by probing each G4Step which marked the end of a secondary particle's track for the particle name.
+Gamma rays (indicitive of secondary electron production), as well as $n\times m$ combinations of secondary protons and neutrons for $n,m:\mathcal{Z}\in[1,5], \lq 5+'$ were tallied per event.
+Each G4Run ended with an averaging of the productions combinations by event per energy and geometry, normalizing the result such that $\sum_n \sum_m P(n,m) = 1$.
 
@@
 
+\section{References}
+\begin{thebibliography}{99}
+
+\bibitem[1]{Geant4:physicsList}
+\lq\lq Use cases - Reference Physics Lists." \\
+Geant4 Online User Support. \\
+\url{http://www.geant4.org/geant4/support/proc_mod_catalog/physics_lists/useCases.shtml}
+
+\end{thebibliography}
+
 \end{multicols}

### 2015-03-08 src/cube-to-cyl.cc

@@ -64,6 +64,28 @@ int main(int argc,char** argv) {
   G4MTRunManager * runManager = new G4MTRunManager;
   if ( nThreads > 0 ) { 
     runManager->SetNumberOfThreads(nThreads);
+
+    // Make base dir
+    std::ostringstream dirCommandStream;
+    G4String data_dir = "data/";
+    dirCommandStream << "mkdir -p " << data_dir;
+    G4String dirCommand = dirCommandStream.str();
+    system(dirCommand);
+
+    // Create data/.threads to relay nThreads info
+    // I/O vars
+    std::ostringstream fileNameStream;
+    std::ofstream fileStream;
+    G4String fileName;
+
+    // Open and add nThreads
+    fileNameStream.str(""); fileName = "";
+    fileNameStream << data_dir << ".threads";
+    fileName = fileNameStream.str();
+    std::ofstream threadFile;
+    threadFile.open(fileName);
+    threadFile << nThreads;
+    threadFile.close();
   }  
 #else
   G4RunManager * runManager = new G4RunManager;

### 2015-03-08 src/src/RunAction.cc

@@ -82,8 +82,8 @@ void RunAction::EndOfRunAction(const G4Run* run) {
   G4String data_dir_energy = "E";
   G4String data_dir_analysis = "Analysis";
   
-  // Acqiure state vars
-  G4int Al_side;
+  // Acqiure state and thread vars
+  G4int Al_side, nThreads;
   fileNameStream.str(""); fileName = "";
   fileNameStream << data_dir << ".state";
   fileName = fileNameStream.str();
@@ -91,6 +91,15 @@ void RunAction::EndOfRunAction(const G4Run* run) {
   stateFile.open(fileName);
   stateFile >> fileVarGet;
   Al_side = atoi(fileVarGet);
+  stateFile.close();
+  fileNameStream.str(""); fileVarGet = ""; fileName = "";
+  fileNameStream << data_dir << ".threads";
+  fileName = fileNameStream.str();
+  std::ifstream threadFile;
+  threadFile.open(fileName);
+  threadFile >> fileVarGet;
+  nThreads = atoi(fileVarGet);
+  threadFile.close();
     
   // Primary energy (run) number and total events
   G4int E_Num = run->GetRunID();
@@ -103,7 +112,7 @@ void RunAction::EndOfRunAction(const G4Run* run) {
   // Invoke stat vars  
   G4int zBin, numBins = 1150;
   G4double numProtons = 0, numNeutrons = 0, numGammas = 0;
-  G4double matrixProtonsNeutrons[7][7] = {0};
+  G4double matrixProtonsNeutrons[7][7] = {{0}};
   G4double energy_bins[1150] = {0};
   G4double charge_bins[1150] = {0};
   G4double particleEDep, particleCharge;
@@ -123,11 +132,29 @@ void RunAction::EndOfRunAction(const G4Run* run) {
   std::ifstream tallyFile;
   tallyFile.open(tallyFileName);
 
-  // Final thread: any thread can finish first, so check for numEvents lines of tally
-  G4int number_of_lines = 0;
-  std::ifstream tallyLineTest(tallyFileName);
-  while ( std::getline(tallyLineTest, fileVarGet) ) number_of_lines++;
-  if ( number_of_lines == numEvents ) {
+  // Final thread: any thread can finish first, so check run state file for nThreads of '#'
+  // Add '#' per run
+  G4String threadString, numThreadsString = "";
+  fileNameStream.str(""); fileName = "";
[…]

### 2015-03-08 docs/Paper/paper.tex
Summarizing 3D plot data constructed in run

@@
 \documentclass[11pt]{article}
-\title{Geant4 Benchmark Analysis: Al cube and He cylindrical chamber}
+\title{Geant4 Benchmark Analysis:\\ Al cube and He cylindrical chamber}
 \author{Shaun Marshall}
@@
 This experiment analyzes a setup of interest, firing collimated protons and neutrons in the range of $10^0-5\cdot10^8\ eV$ at an aluminum box 50 cm away of side 5, 10, and 25 cm, 50 cm, in front of a cylindrical container of helium 50 cm further.
-The analytical tasks with which to assess and characterize the scenario include an energy deposition map, charge displacemnent map, and particle creation probabilities tables.
+The encoded tasks which assess and characterize the scenario include an energy deposition map, charge displacemnent map, and particle creation probabilities tables.
 Results are comparable to empirical studies of proton dosimetry and demonstrate validity of Geant4 theoretical modeling.
@@
 \section{Introduction}
+
+Geant4 is a Monte Carlo simulation software written in C++, used by many leading research institutions of nuclear and particle physics\cite{?}.
+Components of definition, runtime and analysis are compiled separately as classes located in header files; such generalized object-variables are well-suited for precise and fully customizable geometric and analytical specifications.
 
@@
 
+\vspace{0.25 cm}
 \begin{figurehere}
@@
 \resizebox{\columnwidth}{!}{\includegraphics{../testrun.png}}
-\caption{\label{fig:schematic}\small \emph{Schematic of constructed detector geometry with sample event, using Geant4 OpenGL visualization.}}
+\caption{\small \emph{Schematic of constructed detector geometry with sample event, using Geant4 OpenGL visualization.}}
+\label{fig:schematic}
 \end{figurehere}
+\vspace{0.25 cm}
 
@@
 Probably particle production matrices $P(n,m)$ were constructed by probing each G4Step which marked the end of a secondary particle's track for the particle name.
-Gamma rays (indicitive of secondary electron production), as well as $n\times m$ combinations of secondary protons and neutrons for $n,m:\mathcal{Z}\in[1,5], \lq 5+'$ were tallied per event.
-Each G4Run ended with an averaging of the productions combinations by event per energy and geometry, normalizing the result such that $\sum_n \sum_m P(n,m) = 1$.
+Gamma rays (indicitive of secondary electron production), as well as $n\times m$ combinations of secondary protons and neutrons for $n,m:\mathcal{Z}\in[1,5], \lq 5+$' were tallied per event.
+Each G4Run ended by averaging the productions combinations by event per energy and geometry, normalizing the result such that $\sum_n \sum_m P(n,m) = 1$.
 

### 2015-03-08 src/cube-to-cyl.cc

@@ -184,6 +184,10 @@ int main(int argc,char** argv) {
       UImanager->ApplyCommand(command+macro);
     }
     
+    // Plot all figures
+    G4String runGnuplot = "gnuplot graphs.gplot";
+    system(runGnuplot);
+
     // Remove state flag
     G4String runRm = "rm " + data_dir + ".state";
     system(runRm);

### 2015-03-08 src/src/RunAction.cc

@@ -156,6 +156,21 @@ void RunAction::EndOfRunAction(const G4Run* run) {
   // If fourth run (not ID==4, but the fourth being completed)
   if ( threadString == totalThreadsString ) {
   
+    // Energies for label
+    G4int E_Int = (E_Num % 5); if ( E_Int == 0 ) { E_Int = 5; }
+    std::ostringstream energy_stringStream;
+    energy_stringStream << E_Int;
+    if ( (( E_Num % 15 ) > 5) || (( E_Num % 15) == 0) ) { energy_stringStream << "0"; }
+    if ( (( E_Num % 15 ) > 10) || (( E_Num % 15) == 0) ) { energy_stringStream << "0"; }
+    G4String energy_valString = energy_stringStream.str();
+    G4int energy_val = atoi(energy_valString);
+    if ( ( 15 < E_Num ) && ( E_Num < 31 ) ) { energy_stringStream << " k"; energy_val = energy_val*1000; }
+    if ( ( E_Num > 30 ) && ( E_Num < 46) ) { energy_stringStream << " M"; energy_val = energy_val*1000000; }
+    energy_stringStream << "eV";
+    if ( data_dir_particle == "p" ) { energy_stringStream << " Protons"; }
+    if ( data_dir_particle == "n" ) { energy_stringStream << " Neutrons"; }
+    G4String energy_string = energy_stringStream.str();
+    
     // 1 Energy Deposition
     // Continuously append to energy bins
     while ( getline(energyFile, fileVarGet, ' ') ) {
@@ -192,9 +207,9 @@ void RunAction::EndOfRunAction(const G4Run* run) {
     fileNameStream << data_dir << data_dir_geo << Al_side << "/" << data_dir_particle << data_dir_energy << E_Num << "/bins.dat";
     fileName = fileNameStream.str();
     fileStream.open (fileName, std::ios::app);
-    fileStream << "#  z (mm)   Energy_Dep  Net_Charge\n";
+    fileStream << "# Energy z_(mm) Energy_Dep Net_Charge\n";
     for ( G4int binNum = 0; binNum<numBins; binNum++ ) {
-      fileStream << binNum << " " << energy_bins[binNum]/numEvents << " " << charge_bins[binNum]/numEvents << "\n";
+      fileStream << energy_val << " " << binNum << " " << energy_bins[binNum]/numEvents << " " << charge_bins[binNum]/numEvents << "\n";
     }
     fileStream.close();
[…]

### 2015-03-11 bin/cube-to-cyl.cc
Rehaul of event structuring; slight tweak in production tallies needed

@@ -1,0 +1,224 @@
+#include "DetectorConstruction.hh"
+#include "ActionInitialization.hh"
+
+#ifdef G4MULTITHREADED
+#include "G4MTRunManager.hh"
+#else
+#include "G4RunManager.hh"
+#endif
+
+#include "G4UImanager.hh"
+#include "G4UIcommand.hh"
+
+#include "FTFP_BERT.hh"
+
+#include "Randomize.hh"
+
+#ifdef G4VIS_USE
+#include "G4VisExecutive.hh"
+#endif
+
+#ifdef G4UI_USE
+#include "G4UIExecutive.hh"
+#endif
+
+namespace {
+  void PrintUsage() {
+    G4cerr << " Usage: " << G4endl;
+    G4cerr << " ./cube-to-cyl [-m macro ] [-u UIsession] [-t nThreads]" << G4endl;
+    G4cerr << "   note: -t option is available only for multi-threaded mode."
+           << G4endl;
+  }
+}
+
+int main(int argc,char** argv) {
+  // Evaluate arguments
+  if ( argc > 7 ) {
+    PrintUsage();
+    return 1;
+  }  
+  G4String macro;
+  G4String session;
+#ifdef G4MULTITHREADED
+  G4int nThreads = 0;
+#endif
+  for ( G4int i=1; i<argc; i=i+2 ) {
+    if      ( G4String(argv[i]) == "-m" ) macro = argv[i+1];
+    else if ( G4String(argv[i]) == "-u" ) session = argv[i+1];
+#ifdef G4MULTITHREADED
+    else if ( G4String(argv[i]) == "-t" ) {
+      nThreads = G4UIcommand::ConvertToInt(argv[i+1]);
+    }
+#endif
+    else {
+      PrintUsage();
+      return 1;
+    }
+  }  
+  
+  // Choose the Random engine
+  G4Random::setTheEngine(new CLHEP::RanecuEngine);
+  
+  // Construct the default run manager
+#ifdef G4MULTITHREADED
+  G4MTRunManager * runManager = new G4MTRunManager;
+  if ( nThreads > 0 ) { 
+    runManager->SetNumberOfThreads(nThreads);
+
+    // Make base dir
+    std::ostringstream dirCommandStream;
+    G4String data_dir = "data/";
+    dirCommandStream << "mkdir -p " << data_dir;
+    G4String dirCommand = dirCommandStream.str();
+    system(dirCommand);
+
+    // Create data/.threads to relay nThreads info
[…]

### 2015-03-11 bin/src/EventAction.cc

@@ -1,0 +1,217 @@
+#include "EventAction.hh"
+#include "RunAction.hh"
+#include "Analysis.hh"
+#include "Randomize.hh"
+
+#include "G4RunManager.hh"
+#include "G4Run.hh"
+#include "G4Event.hh"
+#include "G4UnitsTable.hh"
+
+#include <iomanip>
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <stdio.h>
+#include <sys/types.h>
+
+// Useful module inserts
+EventAction::EventAction() : G4UserEventAction() {}
+EventAction::~EventAction() {}
+
+void EventAction::BeginOfEventAction(const G4Event* /*event*/) {}
+
+void EventAction::EndOfEventAction(const G4Event* event) {
+  // Energy scoring
+  //
+  // Acquire statistics normalized per event for each energy
+  //
+  // 1. Total energy deposited per bin
+  // 2. Total charge transfer between bins
+  // 3a. e- backscatter per primary
+  // 3b. p+ created per primary
+  // 3c. n created per primary
+  
+  // I/O vars
+  std::ostringstream geoFileNameStream;
+  std::ifstream geoFileStream;
+  G4String geoFileName;
+
+  std::ostringstream eventFileNameStream;
+  std::ifstream eventFileStream;
+  G4String eventFileName;
+
+  std::ostringstream binsFileNameStream;
+  std::ofstream binsOutFileStream;
+  std::ifstream binsInFileStream;
+  G4String binsFileName;
+
+  std::ostringstream productionFileNameStream;
+  std::ofstream productionOutFileStream;
+  std::ifstream productionInFileStream;
+  G4String productionFileName;
+
+  G4String fileVarGet;
+  G4String runRm;
+  
+  // Directory info vars
+  G4String data_dir = "data/";
+  G4String data_dir_geo = "Al";
+  G4String data_dir_particle = "p";
+  G4String data_dir_energy = "E";
+  G4String data_dir_analysis = "Analysis";
+  G4String data_dir_events = "Events";
+  
+  // Acqiure geometry state vars
+  G4int Al_side;
+  geoFileNameStream << data_dir << ".state";
+  geoFileName = geoFileNameStream.str();
+  geoFileStream.open(geoFileName);
+  geoFileStream >> fileVarGet;
+  Al_side = atoi(fileVarGet);
+    
+  // Primary energy (run) number, event number, and total events
[…]

### 2015-03-11 bin/src/RunAction.cc

@@ -1,0 +1,276 @@
+#include "RunAction.hh"
+#include "PrimaryGeneratorAction.hh"
+#include "Analysis.hh"
+#include "G4Run.hh"
+#include "G4RunManager.hh"
+#include "G4UnitsTable.hh"
+#include "G4SystemOfUnits.hh"
+#include "G4Threading.hh"
+
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <stdio.h>
+#include <unistd.h>
+#include <sys/types.h>
+#include <algorithm>
+
+RunAction::RunAction() : G4UserRunAction() {}
+RunAction::~RunAction() { delete G4AnalysisManager::Instance(); }
+
+void RunAction::BeginOfRunAction(const G4Run* run) {
+  // Primary thread
+  if ( G4Threading::G4GetThreadId() == 0 ) {
+    // Directory info
+    G4String fileVarGet;
+    G4String data_dir = "data/";
+    G4String data_dir_particle = "p";
+
+    // I/O vars
+    std::ostringstream fileNameStream;
+    std::ofstream fileStream;
+    G4String fileName;
+
+    // Acqiure state vars
+    G4int Al_side;
+    fileNameStream.str(""); fileName = "";
+    fileNameStream << data_dir << ".state";
+    fileName = fileNameStream.str();
+    std::ifstream stateFile;
+    stateFile.open(fileName);
+    stateFile >> fileVarGet;
+    Al_side = atoi(fileVarGet);
+
+    // Primary energy (run) number and total events
+    G4int E_Num = run->GetRunID();
+    // Adjust Energy number by state var, beam particle by energy number
+    G4int Al_num = 0;   if ( Al_side == 10 ) Al_num = 1; if ( Al_side == 25 ) Al_num = 2;
+    E_Num = E_Num - Al_num*90 + 1;
+    if ( E_Num > 45 ) { E_Num = E_Num - 45; data_dir_particle = "n"; }
+
+    G4cout << "Running " << data_dir_particle << " energy #" << E_Num << " for Al=" << Al_side << G4endl;
+  }
+}
+
+void RunAction::EndOfRunAction(const G4Run* run) {
+  // Energy scoring
+  //
+  // Acquire statistics normalized per event for each energy
+  //
+  // 1. Total energy deposited per bin
+  // 2. Total charge transfer between bins
+  // 3a. gamma created per primary
+  // 3b. p+ created per primary
[…]

### 2015-03-11 src/cube-to-cyl.cc

@@ -1,217 +1,0 @@
-#include "DetectorConstruction.hh"
-#include "ActionInitialization.hh"
-
-#ifdef G4MULTITHREADED
-#include "G4MTRunManager.hh"
-#else
-#include "G4RunManager.hh"
-#endif
-
-#include "G4UImanager.hh"
-#include "G4UIcommand.hh"
-
-#include "FTFP_BERT.hh"
-
-#include "Randomize.hh"
-
-#ifdef G4VIS_USE
-#include "G4VisExecutive.hh"
-#endif
-
-#ifdef G4UI_USE
-#include "G4UIExecutive.hh"
-#endif
-
-namespace {
-  void PrintUsage() {
-    G4cerr << " Usage: " << G4endl;
-    G4cerr << " ./cube-to-cyl [-m macro ] [-u UIsession] [-t nThreads]" << G4endl;
-    G4cerr << "   note: -t option is available only for multi-threaded mode."
-           << G4endl;
-  }
-}
-
-int main(int argc,char** argv) {
-  // Evaluate arguments
-  if ( argc > 7 ) {
-    PrintUsage();
-    return 1;
-  }  
-  G4String macro;
-  G4String session;
-#ifdef G4MULTITHREADED
-  G4int nThreads = 0;
-#endif
-  for ( G4int i=1; i<argc; i=i+2 ) {
-    if      ( G4String(argv[i]) == "-m" ) macro = argv[i+1];
-    else if ( G4String(argv[i]) == "-u" ) session = argv[i+1];
-#ifdef G4MULTITHREADED
-    else if ( G4String(argv[i]) == "-t" ) {
-      nThreads = G4UIcommand::ConvertToInt(argv[i+1]);
-    }
-#endif
-    else {
-      PrintUsage();
-      return 1;
-    }
-  }  
-  
-  // Choose the Random engine
-  G4Random::setTheEngine(new CLHEP::RanecuEngine);
-  
-  // Construct the default run manager
-#ifdef G4MULTITHREADED
-  G4MTRunManager * runManager = new G4MTRunManager;
-  if ( nThreads > 0 ) { 
-    runManager->SetNumberOfThreads(nThreads);
-
-    // Make base dir
-    std::ostringstream dirCommandStream;
-    G4String data_dir = "data/";
-    dirCommandStream << "mkdir -p " << data_dir;
-    G4String dirCommand = dirCommandStream.str();
-    system(dirCommand);
-
-    // Create data/.threads to relay nThreads info
[…]

### 2015-03-11 src/src/EventAction.cc

@@ -1,163 +1,0 @@
-#include "EventAction.hh"
-#include "RunAction.hh"
-#include "Analysis.hh"
-#include "Randomize.hh"
-
-#include "G4RunManager.hh"
-#include "G4Run.hh"
-#include "G4Event.hh"
-#include "G4UnitsTable.hh"
-
-#include <iomanip>
-#include <iostream>
-#include <fstream>
-#include <string>
-#include <stdio.h>
-#include <sys/types.h>
-
-// Useful module inserts
-EventAction::EventAction() : G4UserEventAction() {}
-EventAction::~EventAction() {}
-
-void EventAction::BeginOfEventAction(const G4Event* /*event*/) {}
-
-void EventAction::EndOfEventAction(const G4Event* event) {
-  // Energy scoring
-  //
-  // Acquire statistics normalized per event for each energy
-  //
-  // 1. Total energy deposited per bin
-  // 2. Total charge transfer between bins
-  // 3a. e- backscatter per primary
-  // 3b. p+ created per primary
-  // 3c. n created per primary
-  
-  // I/O vars
-  std::ostringstream fileNameStream;
-  std::ofstream fileStream;
-  G4String fileName;
-  std::ostringstream energyFileNameStream;
-  G4String energyFileName;
-  std::ostringstream chargeFileNameStream;
-  G4String chargeFileName;
-  std::ostringstream tallyFileNameStream;
-  G4String tallyFileName;
-  G4String runRm;
-  
-  // Directory info
-  G4String fileVarGet;
-  G4String data_dir = "data/";
-  G4String data_dir_geo = "Al";
-  G4String data_dir_particle = "p";
-  G4String data_dir_energy = "E";
-  G4String data_dir_analysis = "Analysis";
-  
-  // Acqiure state vars
-  G4int Al_side;
-  fileNameStream.str(""); fileName = "";
-  fileNameStream << data_dir << ".state";
-  fileName = fileNameStream.str();
-  std::ifstream stateFile;
-  stateFile.open(fileName);
-  stateFile >> fileVarGet;
-  Al_side = atoi(fileVarGet);
-    
-  // Primary energy (run) number and event number
-  G4int E_Num = G4RunManager::GetRunManager()->GetCurrentRun()->GetRunID();
-  G4int eventNum = event->GetEventID();
-  // Adjust Energy number by state var, beam particle by energy number
[…]

### 2015-03-11 src/src/RunAction.cc

@@ -1,264 +1,0 @@
-#include "RunAction.hh"
-#include "PrimaryGeneratorAction.hh"
-#include "Analysis.hh"
-#include "G4Run.hh"
-#include "G4RunManager.hh"
-#include "G4UnitsTable.hh"
-#include "G4SystemOfUnits.hh"
-#include "G4Threading.hh"
-
-#include <iostream>
-#include <fstream>
-#include <string>
-#include <stdio.h>
-#include <unistd.h>
-#include <sys/types.h>
-#include <algorithm>
-
-RunAction::RunAction() : G4UserRunAction() {}
-RunAction::~RunAction() { delete G4AnalysisManager::Instance(); }
-
-void RunAction::BeginOfRunAction(const G4Run* run) {
-  // Primary thread
-  if ( G4Threading::G4GetThreadId() == 0 ) {
-    // Directory info
-    G4String fileVarGet;
-    G4String data_dir = "data/";
-    G4String data_dir_particle = "p";
-
-    // I/O vars
-    std::ostringstream fileNameStream;
-    std::ofstream fileStream;
-    G4String fileName;
-
-    // Acqiure state vars
-    G4int Al_side;
-    fileNameStream.str(""); fileName = "";
-    fileNameStream << data_dir << ".state";
-    fileName = fileNameStream.str();
-    std::ifstream stateFile;
-    stateFile.open(fileName);
-    stateFile >> fileVarGet;
-    Al_side = atoi(fileVarGet);
-
-    // Primary energy (run) number and total events
-    G4int E_Num = run->GetRunID();
-    // Adjust Energy number by state var, beam particle by energy number
-    G4int Al_num = 0;   if ( Al_side == 10 ) Al_num = 1; if ( Al_side == 25 ) Al_num = 2;
-    E_Num = E_Num - Al_num*90 + 1;
-    if ( E_Num > 45 ) { E_Num = E_Num - 45; data_dir_particle = "n"; }
-
-    G4cout << "Running " << data_dir_particle << " energy #" << E_Num << " for Al=" << Al_side << G4endl;
-  }
-}
-
-void RunAction::EndOfRunAction(const G4Run* run) {
-  // Energy scoring
-  //
-  // Acquire statistics normalized per event for each energy
-  //
-  // 1. Total energy deposited per bin
-  // 2. Total charge transfer between bins
-  // 3a. gamma created per primary
-  // 3b. p+ created per primary
-  // 3c. n created per primary
-  
-  // I/O vars
-  std::ostringstream fileNameStream;
[…]

### 2015-03-11 bin/src/RunAction.cc
Correct counting and no under/overflow; finally ready for segfaultless long run

@@ -135,7 +135,7 @@ void RunAction::EndOfRunAction(const G4Run* run) {
 
   // Acquire nThreads string of '#'s
   std::ostringstream numThreadsStream;
-  for (G4int numThreads_i=1; numThreads_i < nThreads; numThreads_i++) { numThreadsStream << "#"; }
+  for (G4int numThreads_i=0; numThreads_i < nThreads; numThreads_i++) { numThreadsStream << "#"; }
   G4String totalThreadsString = numThreadsStream.str();
 
   // If fourth run (not ID==4, but the fourth being completed [future work: thread merge class via G4MTRunManager])
@@ -162,8 +162,8 @@ void RunAction::EndOfRunAction(const G4Run* run) {
         // Iteratively reconstruct energy/charge_bins, ignoring energy_val
         while ( getline(binsInFileStream, fileVarGet, ' ') ) {
           getline(binsInFileStream, fileVarGet, ' '); zBin = atoi(fileVarGet);
-          getline(binsInFileStream, fileVarGet, ' '); energy_bins[zBin] = atof(fileVarGet);
-          getline(binsInFileStream, fileVarGet); charge_bins[zBin] = atof(fileVarGet);
+          getline(binsInFileStream, fileVarGet, ' '); energy_bins[zBin] += atof(fileVarGet);
+          getline(binsInFileStream, fileVarGet); charge_bins[zBin] += atof(fileVarGet);
         }
         binsInFileStream.close();
       }
@@ -173,32 +173,28 @@ void RunAction::EndOfRunAction(const G4Run* run) {
       productionFileNameStream << data_dir << data_dir_geo << Al_side << "/" << data_dir_particle << data_dir_energy << E_Num << "/" << data_dir_events << "/production" << eventNum_i << ".dat";
       productionFileName = productionFileNameStream.str();
       productionInFileStream.open(productionFileName);
-      if ( productionInFileStream.good() ) {
-        // Acquire Gamma count, ignore header (1st, rest of 2nd, 3rd)
-        getline(productionInFileStream, fileVarGet);
-        getline(productionInFileStream, fileVarGet, ' ');
-        getline(productionInFileStream, fileVarGet, ' ');
-        numGammas = atof(fileVarGet);
-        getline(productionInFileStream, fileVarGet);
-        getline(productionInFileStream, fileVarGet);
+      
[…]

### 2015-03-14 docs/Paper/paper.tex
Cleaned up repo, full graph output, revised paper with results

@@
 \date{\today}
+\usepackage{amsmath, amssymb}
 \usepackage{abstract}
+\usepackage{subcaption}
 \usepackage{multicol}
@@
 
-Geant4 is a Monte Carlo simulation software written in C++, used by many leading research institutions of nuclear and particle physics\cite{?}.
+Geant4 is a Monte Carlo simulation software written in C++, used by many leading research institutions of nuclear and particle physics\cite{Geant4:applications}.
 Components of definition, runtime and analysis are compiled separately as classes located in header files; such generalized object-variables are well-suited for precise and fully customizable geometric and analytical specifications.
 
-\section{Procedure}
+\section{Methodology}
 
-1 million simulated events of collimated protons and neutrons were fired 50 cm to an Aluminum block in a vacuous world, which lie 50 cm in front of a cylindrical He gas chamber centered in line with the block vertically, perpendicular to the cylinder's long axis (fig~\ref{fig:schematic}).
+1 million simulated events of collimated protons and neutrons were fired 50 cm to an Aluminum block in a vacuous world, which lie 50 cm in front of a cylindrical He gas chamber (of height 50 cm and radius 15 cm) centered in line with the block vertically, perpendicular to the cylinder's long axis (fig~\ref{fig:schematic}).
 This geometry was iterated for the 5, 10 and 25 cm side lengths of the block.
@@
 \centering
-\resizebox{\columnwidth}{!}{\includegraphics{../testrun.png}}
+\resizebox{\columnwidth}{!}{\includegraphics{pics/testrun.png}}
 \caption{\small \emph{Schematic of constructed detector geometry with sample event, using Geant4 OpenGL visualization.}}
@@
 
-The FTFP\_BERT physics list was utilized\cite{Geant4:physicsList}, with track cuts at a 10 micron minimum step legnth.
+The FTFP\_BERT 2.0 physics list was activated\cite{Geant4:physicsList}, with track cuts at a 10 micron minimum step legnth.
 Primary particle energies range from $1$ to $5\cdot10^x$, where $x:\mathcal{Z}\in[0,8]$.
@@
 
-\section{Discussion}
+\section{Results}
+
+Energy deposition signatures were acquired for protons and neutrons.
+Figures \ref{fig:pEDep_eV} and \ref{fig:pEDep_keV} show a monotonically increaing function of energy deposition across the experimental distance $z$ for protons in the eV to keV range.
+The MeV-range (fig~\ref{fig:pEDep_MeV}) uniquely depicts a peak around 50 MeV before sharply declining throughout the next order of magnitude.
+The Aluminum cube volume, which exists in the range (57.5 cm $\pm$ $L_{Al}$) where $L_{Al}=5,10,25$ cm, receives virtually all protons until MeV-range energies.
+Up to 20 MeV, the total energy is deposited at $z=57.5 cm - L_{Al}$, after which the total deposition extends further in the $+z$ direction.
+The last decade of energy probed exibits a dramatic increase in this extension.
+
+%% Proton EDep figures
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pEDep_eV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per eV-range proton}}
+\label{fig:pEDep_eV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pEDep_keV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per keV-range proton}}
+\label{fig:pEDep_keV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pEDep_MeV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per MeV-range proton}}
+\label{fig:pEDep_MeV}
+\end{figurehere}
+\vspace{0.15 cm}
+
+%% Neutron EDep figures
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nEDep_eV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per eV-range neutron}}
+\label{fig:nEDep_eV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nEDep_keV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per keV-range neutron}}
+\label{fig:nEDep_keV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nEDep_MeV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per MeV-range neutron}}
+\label{fig:nEDep_MeV}
+\end{figurehere}
+\vspace{0.15 cm}
+
+Neutron energy deposition maps are found in figures \ref{fig:nEDep_eV}, \ref{fig:nEDep_keV}, and \ref{fig:nEDep_MeV}, following the same energy labeling schema.
+The total energy deposition here also seems to monotonically increase until MeV-range energies, at which point the deposition sputters with distance.
 
@@
 
-\section{References}
 \begin{thebibliography}{99}
 
-\bibitem[1]{Geant4:physicsList}
+\bibitem[1]{Geant4:applications}
+Geant4 Applications. \\
+\url{http://geant4.web.cern.ch/geant4/applications/index.shtml}
+
+\bibitem[2]{Geant4:physicsList}
 \lq\lq Use cases - Reference Physics Lists." \\

### 2015-03-14 bin/cube-to-cyl.cc

@@ -129,6 +129,7 @@ int main(int argc,char** argv) {
     G4cout << "Creating data analysis tree..." << G4endl;
     std::ostringstream dirCommandStream;
     G4String data_dir = "data/";
+    G4String data_dir_figs = "figs/";
     G4String data_dir_geo = "Al";
     G4String data_dir_particle = "p";
     G4String data_dir_energy = "E";
@@ -136,7 +137,7 @@ int main(int argc,char** argv) {
     G4String data_dir_events = "Events";
 
     // Make base dir
-    dirCommandStream << "mkdir -p " << data_dir;
+    dirCommandStream << "mkdir -p " << data_dir << " " << data_dir_figs;
     G4String dirCommand = dirCommandStream.str();
     system(dirCommand);
 

### 2015-03-14 bin/src/RunAction.cc

@@ -202,7 +202,7 @@ void RunAction::EndOfRunAction(const G4Run* run) {
     if ( (( E_Num % 15 ) > 5) || (( E_Num % 15) == 0) ) { energy_stringStream << "0"; }
     if ( (( E_Num % 15 ) > 10) || (( E_Num % 15) == 0) ) { energy_stringStream << "0"; }
     G4String energy_valString = energy_stringStream.str();
-    G4int energy_val = atoi(energy_valString);
+    G4double energy_val = atof(energy_valString);
     if ( ( 15 < E_Num ) && ( E_Num < 31 ) ) { energy_stringStream << " k"; energy_val = energy_val*1000; }
     if ( ( E_Num > 30 ) && ( E_Num < 46) ) { energy_stringStream << " M"; energy_val = energy_val*1000000; }
     energy_stringStream << "eV";

### 2015-03-14 bin/cube-to-cyl.cc
Geometries figure update

@@ -144,7 +144,7 @@ int main(int argc,char** argv) {
     // Geometry dir iteration
     for (G4int al_num=0; al_num<3; al_num++) {
       dirCommandStream.str(""); dirCommand = "";
-      dirCommandStream << "mkdir -p " << data_dir << data_dir_geo << Al_side[al_num] << "/";
+      dirCommandStream << "mkdir -p " << data_dir << data_dir_geo << Al_side[al_num] << "/ " << data_dir_figs << data_dir_geo << Al_side[al_num] << "/";
       dirCommand = dirCommandStream.str();
       system(dirCommand);
       

### 2015-03-14 docs/Paper/paper.tex
Results and appendices revision, still waiting on large run

@@
 
+\subsection{Energy Deposition}
+
 Energy deposition signatures were acquired for protons and neutrons.
@@
 The MeV-range (fig~\ref{fig:pEDep_MeV}) uniquely depicts a peak around 50 MeV before sharply declining throughout the next order of magnitude.
-The Aluminum cube volume, which exists in the range (57.5 cm $\pm$ $L_{Al}$) where $L_{Al}=5,10,25$ cm, receives virtually all protons until MeV-range energies.
-Up to 20 MeV, the total energy is deposited at $z=57.5 cm - L_{Al}$, after which the total deposition extends further in the $+z$ direction.
-The last decade of energy probed exibits a dramatic increase in this extension.
+The Aluminum cube volume, which exists in the range (57.5 cm $\pm$ $L_{Al}/2$) where $L_{Al}=5,10,25$ cm, receives virtually all protons until MeV-range energies.
+Up to 20 MeV, the total energy is deposited at $z=57.5 cm - L_{Al}/2$, after which the total deposition extends further in the $+z$ direction.
+The last decade of energy probed exibits a dramatic increase in this extension, which increasingly exposes a gradual incline to a peak followed by a drop.
 
@@
 \end{figurehere}
+\vspace{0.2 cm}
+
+Neutron energy deposition maps are found in figures \ref{fig:nEDep_eV}, \ref{fig:nEDep_keV}, and \ref{fig:nEDep_MeV}, following the same energy labeling schema.
+The total energy deposition here also seems to monotonically increase until MeV-range energies, at which point the deposition sputters across various locations throughout the $57.5 cm \pm L_{Al}/2$ domain in $z$.
+See Appendix~\ref{app:EDep} for energy deposition figures for secondary and tertiary geometric models, omitted for behavioral redundancy.
+
+\subsection{Charge Deposition}
+
+The average charge displacement per proton event is acquired and normalized by the gain equation (eqn.~\ref{eqn:gain}) in order to create a charge displacement landscapes.
+\begin{equation}
+  gain[z] = \frac{\sum \text{\emph{net charge @ $z$}} }{\sum \text{\emph{charge of primary particle}} } \label{eqn:gain}
+\end{equation}
+Up to around 10 keV proton energies (figs.~\ref{fig:pChargeDep_eV} and \ref{fig:pChargeDep_keV}) the nominal gain outside of the defined volumes (hence in air) are comparable to the magnitudes found between the boundaries of the Aluminum block.
+Beyond 100 MeV proton energies (fig.~\ref{fig:pChargeDep_MeV}) a gain measurement may be found within the confines of the Helium cylinder, which exists within the range $z=100 cm \pm R_{He}$; for these figures, a large peak may be seen at the world's edge, $z=115 cm$.
+The $-1e$ net gain at $z=0$ for all figures is where the collimated source originates.
+
+No visible charge trasfer occurs with neutron primary events in the ev to keV energy range (figs.~\ref{fig:nChargeDep_eV} and \ref{fig:nChargeDep_keV}).
+Only in MeV range beam energies (fig.~\ref{fig:nChargeDep_MeV}) do the neutron events charge transfer at the boundaries of both the Aluminum cube and Helium cylinder.
+See Appendix~\ref{app:ChargeDep} for charge deposition figures for secondary and tertiary geometric models, omitted for behavioral redundancy.
+
+%% Proton ChargeDep figures
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pChargeDep_eV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per eV-range proton}}
+\label{fig:pChargeDep_eV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pChargeDep_keV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per keV-range proton}}
+\label{fig:pChargeDep_keV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pChargeDep_MeV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per MeV-range proton}}
+\label{fig:pChargeDep_MeV}
+\end{figurehere}
 \vspace{0.15 cm}
 
-Neutron energy deposition maps are found in figures \ref{fig:nEDep_eV}, \ref{fig:nEDep_keV}, and \ref{fig:nEDep_MeV}, following the same energy labeling schema.
-The total energy deposition here also seems to monotonically increase until MeV-range energies, at which point the deposition sputters with distance.
+%% Neutron ChargeDep figures
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nChargeDep_eV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per eV-range neutron}}
+\label{fig:nChargeDep_eV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nChargeDep_keV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per keV-range neutron}}
+\label{fig:nChargeDep_keV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nChargeDep_MeV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per MeV-range neutron}}
+\label{fig:nChargeDep_MeV}
+\end{figurehere}
+\vspace{0.15 cm}
 
-\section{Conclusion}
+\subsection{Production Probabilities}
+
+\section{Conclusions}
 
@@
 \end{multicols}
+
+\appendix
+\newpage
+\section{Energy deposition for Al side = 10, 25 cm}\label{app:EDep}
+
+\newpage
+\section{Charge deposition for Al side = 10, 25 cm}\label{app:ChargeDep}
+
 \end{document}

### 2015-03-14 docs/Paper/paper.tex
Revised results, conclusions, simulation results pending...

@@
 
-\subsection{Production Probabilities}
+\subsection{Production Tallies}
+
+There are no protons, neutrons nor gammas produced under 30 MeV proton beam energy, at which the number of gammas created per proton gradually increases with energy.
+The first run which produced \emph{any} proton-neutron combination in any of the geometric setups occured at 200 MeV.
+Particles production tallies for protons at 500 MeV are shown in tables \ref{tab:production_pAl5}, \ref{tab:production_pAl10}, and \ref{tab:production_pAl25}.
+
+\vspace{0.15 cm}
+\begin{tablehere}\begin{centering}
+  \caption{\small \emph{Particle production combination probabilities per 500 MeV proton with $L_{Al}=5 cm$}}
+  \begin{tabular}{c || c c c c c c c}
+    p vs. n & 0 & 1 & 2 & 3 & 4 & 5 & $>$5 \\
+    \hline\hline
+    0 & 1.2 & 0 & 0 & 0 & 0 & 0 & 0 \\
+    1 & 0.1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+    2 & 0.1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+    3 & 0.1 & 0.1 & 0.1 & 0.1 & 0.6 & 0 & 0 \\
+    4 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
+    5 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
+    $>$5 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
+    \hline\hline
+  \end{tabular}
+  \begin{tabular}{r} Gammas: 1.2 \end{tabular}  
+  \label{tab:production_pAl5}
+\end{centering}\end{tablehere}
+\vspace{0.15 cm}
+\begin{tablehere}\begin{centering}
+  \caption{\small \emph{Particle production combination probabilities per 500 MeV proton with $L_{Al}=10 cm$}}
+  \begin{tabular}{c || c c c c c c c}
+    p vs. n & 0 & 1 & 2 & 3 & 4 & 5 & $>$5 \\
+    \hline\hline
+    0 & 1.2 & 0 & 0 & 0 & 0 & 0 & 0 \\
+    1 & 0.1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+    2 & 0.1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+    3 & 0.1 & 0.1 & 0.1 & 0.1 & 0.6 & 0 & 0 \\
+    4 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
+    5 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
+    $>$5 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
+    \hline\hline
+  \end{tabular}
+  \begin{tabular}{r} Gammas: 1.2 \end{tabular}  
+  \label{tab:production_pAl10}
+\end{centering}\end{tablehere}
+\vspace{0.15 cm}
+\begin{tablehere}\begin{centering}
+  \caption{\small \emph{Particle production combination probabilities per 500 MeV proton with $L_{Al}=25 cm$}}
+  \begin{tabular}{c || c c c c c c c}
+    p vs. n & 0 & 1 & 2 & 3 & 4 & 5 & $>$5 \\
+    \hline\hline
+    0 & 1.2 & 0 & 0 & 0 & 0 & 0 & 0 \\
+    1 & 0.1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+    2 & 0.1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+    3 & 0.1 & 0.1 & 0.1 & 0.1 & 0.6 & 0 & 0 \\
+    4 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
+    5 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
+    $>$5 & 0.1 & 0 & 0 & 0 & 0.1 & 0 & 0 \\
+    \hline\hline
+  \end{tabular}
+  \begin{tabular}{r} Gammas: 1.2 \end{tabular}  
+  \label{tab:production_pAl25}
+\end{centering}\end{tablehere}
+\vspace{0.15 cm}
 
 \section{Conclusions}
+
+High energy protons were necessary to penetrate the Aluminum cube and consequentially bring visibility to the Bragg curve, characterized by the stopping power of protons in each media due to pathway ionization.
+The total energy deposited into the volumes curiously seems to decrease beyond the peak with respect to beam energy in figure \ref{fig:pEDep_MeV}; what occurs here is a complete transmission of proportionately many protons through the Aluminum cube, and a continued travel of the protons into the Helium chamber, seen by the demonstrative schematic (fig.~\ref{fig:schematic}).
+This phenomena reappears in the charge deposition landscape of protons at high energies (fig.~\ref{fig:pChargeDep_MeV}), where we observe a conspicuous gain at the world's edge, $z=115cm$; the protons must then tramsmit directly through the Helium chamber to the edge of the defined world where the fine $z$-bin collects the charge of the primary.
+
+Neutrons, which do not ionize their penetration pathways, do not behave with a Bragg curve but rather undergo elastic scattering and nuclear interactions.
+The destructive recoil is seen by the sporadic energy depositions into the Aluminum cube (figs.~\ref{fig:nEDep_eV}, \ref{fig:nEDep_keV}, \ref{fig:nEDep_MeV}).
+Relatively few high energy neutrons are also found to transmit directly through the cube, evidenced by the small shifts in charge deposiition (fig.~\ref{fig:nChargeDep_MeV}) due to obliterated electrons travelling but tens of microns.
 

### 2015-03-15 docs/Paper/paper.tex
Run and paper revision complete

--- 2015-03-14 docs/Paper/paper.tex
@@
 Energy deposition signatures were acquired for protons and neutrons.
-Figures \ref{fig:pEDep_eV} and \ref{fig:pEDep_keV} show a monotonically increaing function of energy deposition across the experimental distance $z$ for protons in the eV to keV range.
-The MeV-range (fig~\ref{fig:pEDep_MeV}) uniquely depicts a peak around 50 MeV before sharply declining throughout the next order of magnitude.
+Figures \ref{fig:pEDep_Al5_eV} and \ref{fig:pEDep_Al5_keV} show a monotonically increaing function of energy deposition across the experimental distance $z$ for protons in the eV to keV range.
+The MeV-range (fig~\ref{fig:pEDep_Al5_MeV}) uniquely depicts a peak around 50 MeV before sharply declining throughout the next order of magnitude.
 The Aluminum cube volume, which exists in the range (57.5 cm $\pm$ $L_{Al}/2$) where $L_{Al}=5,10,25$ cm, receives virtually all protons until MeV-range energies.
@@
 \centering
-\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pEDep_eV.png}}
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_pEDep_eV.png}}
 \caption{\small \emph{Energy deposition landscape (MeV) per eV-range proton}}
-\label{fig:pEDep_eV}
+\label{fig:pEDep_Al5_eV}
 \end{figurehere}
@@
 \centering
-\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pEDep_keV.png}}
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_pEDep_keV.png}}
 \caption{\small \emph{Energy deposition landscape (MeV) per keV-range proton}}
-\label{fig:pEDep_keV}
+\label{fig:pEDep_Al5_keV}
 \end{figurehere}
@@
 \centering
-\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pEDep_MeV.png}}
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_pEDep_MeV.png}}
 \caption{\small \emph{Energy deposition landscape (MeV) per MeV-range proton}}
-\label{fig:pEDep_MeV}
+\label{fig:pEDep_Al5_MeV}
 \end{figurehere}
@@
 \centering
-\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nEDep_eV.png}}
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_nEDep_eV.png}}
 \caption{\small \emph{Energy deposition landscape (MeV) per eV-range neutron}}
-\label{fig:nEDep_eV}
+\label{fig:nEDep_Al5_eV}
 \end{figurehere}
@@
 \centering
-\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nEDep_keV.png}}
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_nEDep_keV.png}}
 \caption{\small \emph{Energy deposition landscape (MeV) per keV-range neutron}}
-\label{fig:nEDep_keV}
+\label{fig:nEDep_Al5_keV}
 \end{figurehere}
@@
 \centering
-\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nEDep_MeV.png}}
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_nEDep_MeV.png}}
 \caption{\small \emph{Energy deposition landscape (MeV) per MeV-range neutron}}
-\label{fig:nEDep_MeV}
+\label{fig:nEDep_Al5_MeV}
 \end{figurehere}
@@
 
-Neutron energy deposition maps are found in figures \ref{fig:nEDep_eV}, \ref{fig:nEDep_keV}, and \ref{fig:nEDep_MeV}, following the same energy labeling schema.
-The total energy deposition here also seems to monotonically increase until MeV-range energies, at which point the deposition sputters across various locations throughout the $57.5 cm \pm L_{Al}/2$ domain in $z$.
+Neutron energy deposition maps are found in figures \ref{fig:nEDep_Al5_eV}, \ref{fig:nEDep_Al5_keV}, and \ref{fig:nEDep_Al5_MeV}, following the same energy labeling schema.
+The total energy deposition here seems to monotonically increase indefinitely; upon reaching MeV-range energies, deposition distributes itself relatively evenly with a bias towards the right across the $57.5 cm \pm L_{Al}/2$ domain in $z$.
 See Appendix~\ref{app:EDep} for energy deposition figures for secondary and tertiary geometric models, omitted for behavioral redundancy.
@@
 \begin{equation}
-  gain[z] = \frac{\sum \text{\emph{net charge @ $z$}} }{\sum \text{\emph{charge of primary particle}} } \label{eqn:gain}
+  gain[z] = \frac{\sum \text{\emph{net charge @ z}} }{\sum \text{\emph{charge of primary particle}} } \label{eqn:gain}
 \end{equation}
-Up to around 10 keV proton energies (figs.~\ref{fig:pChargeDep_eV} and \ref{fig:pChargeDep_keV}) the nominal gain outside of the defined volumes (hence in air) are comparable to the magnitudes found between the boundaries of the Aluminum block.
-Beyond 100 MeV proton energies (fig.~\ref{fig:pChargeDep_MeV}) a gain measurement may be found within the confines of the Helium cylinder, which exists within the range $z=100 cm \pm R_{He}$; for these figures, a large peak may be seen at the world's edge, $z=115 cm$.
+Up to around 10 keV proton energies (figs.~\ref{fig:pChargeDep_Al5_eV} and \ref{fig:pChargeDep_Al5_keV}) the nominal gain outside of the defined volumes (hence in air) are comparable to the magnitudes found between the boundaries of the Aluminum block.
+Beyond 100 MeV proton energies (fig.~\ref{fig:pChargeDep_Al5_MeV}) a gain measurement may be found within the confines of the Helium cylinder, which exists within the range $z=100 cm \pm R_{He}$; for these figures, a large peak may be seen at the world's edge, $z=115 cm$.
 The $-1e$ net gain at $z=0$ for all figures is where the collimated source originates.
 
-No visible charge trasfer occurs with neutron primary events in the ev to keV energy range (figs.~\ref{fig:nChargeDep_eV} and \ref{fig:nChargeDep_keV}).
-Only in MeV range beam energies (fig.~\ref{fig:nChargeDep_MeV}) do the neutron events charge transfer at the boundaries of both the Aluminum cube and Helium cylinder.
+No visible charge trasfer occurs with neutron primary events in the ev to keV energy range (figs.~\ref{fig:nChargeDep_Al5_eV} and \ref{fig:nChargeDep_Al5_keV}).
+Only in MeV range beam energies (fig.~\ref{fig:nChargeDep_Al5_MeV}) do the neutron events charge transfer at the boundaries of both the Aluminum cube and Helium cylinder.
 See Appendix~\ref{app:ChargeDep} for charge deposition figures for secondary and tertiary geometric models, omitted for behavioral redundancy.
@@
 \centering
-\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pChargeDep_eV.png}}
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_pChargeDep_eV.png}}
 \caption{\small \emph{Charge displacement landscape (gain) per eV-range proton}}
-\label{fig:pChargeDep_eV}
+\label{fig:pChargeDep_Al5_eV}
 \end{figurehere}
@@
 \centering
-\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pChargeDep_keV.png}}
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_pChargeDep_keV.png}}
 \caption{\small \emph{Charge displacement landscape (gain) per keV-range proton}}
-\label{fig:pChargeDep_keV}
+\label{fig:pChargeDep_Al5_keV}
 \end{figurehere}
@@
 \centering
-\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_pChargeDep_MeV.png}}
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_pChargeDep_MeV.png}}
 \caption{\small \emph{Charge displacement landscape (gain) per MeV-range proton}}
-\label{fig:pChargeDep_MeV}
+\label{fig:pChargeDep_Al5_MeV}
 \end{figurehere}
@@
 \centering
-\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nChargeDep_eV.png}}
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_nChargeDep_eV.png}}
 \caption{\small \emph{Charge displacement landscape (gain) per eV-range neutron}}
-\label{fig:nChargeDep_eV}
+\label{fig:nChargeDep_Al5_eV}
 \end{figurehere}
@@
 \centering
-\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nChargeDep_keV.png}}
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_nChargeDep_keV.png}}
 \caption{\small \emph{Charge displacement landscape (gain) per keV-range neutron}}
-\label{fig:nChargeDep_keV}
+\label{fig:nChargeDep_Al5_keV}
 \end{figurehere}
@@
 \centering
-\resizebox{\columnwidth}{!}{\includegraphics{pics/fig_nChargeDep_MeV.png}}
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al5/fig_nChargeDep_MeV.png}}
 \caption{\small \emph{Charge displacement landscape (gain) per MeV-range neutron}}
-\label{fig:nChargeDep_MeV}
+\label{fig:nChargeDep_Al5_MeV}
 \end{figurehere}
@@
 
-\subsection{Production Probabilities}
+\end{multicols}
+\newpage
+\subsection{Production Tallies}
 
+There are no protons, neutrons nor gammas produced under 30 MeV proton beam energy, at which the number of gammas created per proton gradually increases with energy.
+The first run which produced \emph{any} proton-neutron combination in any of the geometric setups occured at 200 MeV.
+Particles production tallies for protons at 500 MeV are shown in tables \ref{tab:production_pAl5}, \ref{tab:production_pAl10}, and \ref{tab:production_pAl25}.
+
+\vspace{0.15 cm}
+\begin{tablehere}\begin{centering}
+  \caption{\small \emph{Particle production combination probabilities per 500 MeV proton with $L_{Al}=5 cm$} (unnormalized)}
+  \begin{tabular}{c || c c c c c c c}
+    p vs. n & 0 & 1 & 2 & 3 & 4 & 5 & $>$5 \\
+    \hline\hline
+    0 & 1.0732 & 0.0043 & 0.0009 & 0.0004 & 0 & 0 & 0 \\
+    1 & 0.204 & 0.0453 & 0.0117 & 0.0082 & 0.005 & 0.0003 & 0.0024 \\
+    2 & 0.1664 & 0.0493 & 0.0482 & 0.0138 & 0.0055 & 0.0028 & 0.0055 \\
+    3 & 0.0888 & 0.0227 & 0.0324 & 0.0159 & 0.0071 & 0.0044 & 0.003 \\
+    4 & 0.0476 & 0.0212 & 0.0259 & 0.021 & 0.0193 & 0.0127 & 0.0076 \\
+    5 & 0.0221 & 0.0079 & 0.0073 & 0.0092 & 0.011 & 0.0068 & 0.0105 \\
+    $>$5 & 0.0141 & 0.0065 & 0.0067 & 0.0067 & 0.0092 & 0.0074 & 0.0195 \\
+    \hline\hline
+  \end{tabular} \\
+  \begin{tabular}{r} Gammas: 1.0737 \end{tabular}
+  \label{tab:production_pAl5}
+\end{centering}\end{tablehere}
+\vspace{0.15 cm}
+\begin{tablehere}\begin{centering}
+  \caption{\small \emph{Particle production combination probabilities per 500 MeV proton with $L_{Al}=10 cm$}}
+  \begin{tabular}{c || c c c c c c c}
+    p vs. n & 0 & 1 & 2 & 3 & 4 & 5 & $>$5 \\
+    \hline\hline
+    0 & 1.0494 & 0.0045 & 0.0015 & 0.0001 & 0.0001 & 0.0001 & 0.0004 \\
+    1 & 0.225 & 0.0462 & 0.0115 & 0.0078 & 0.0044 & 0.0022 & 0.0001 \\
+    2 & 0.1848 & 0.0576 & 0.0534 & 0.0183 & 0.0098 & 0.0027 & 0.0012 \\
+    3 & 0.0942 & 0.0215 & 0.0309 & 0.0218 & 0.0075 & 0.0058 & 0.0035 \\
+    4 & 0.0557 & 0.0192 & 0.0264 & 0.0198 & 0.0231 & 0.0124 & 0.0154 \\
+    5 & 0.0238 & 0.0067 & 0.0068 & 0.0073 & 0.0095 & 0.0074 & 0.0071 \\
+    $>$5 & 0.0173 & 0.0094 & 0.0089 & 0.0089 & 0.0086 & 0.0087 & 0.018 \\
+    \hline\hline
+  \end{tabular} \\
+  \begin{tabular}{r} Gammas: 1.0871 \end{tabular}  
+  \label{tab:production_pAl10}
+\end{centering}\end{tablehere}
+\vspace{0.15 cm}
+\begin{tablehere}\begin{centering}
+  \caption{\small \emph{Particle production combination probabilities per 500 MeV proton with $L_{Al}=25 cm$}}
+  \begin{tabular}{c || c c c c c c c}
+    p vs. n & 0 & 1 & 2 & 3 & 4 & 5 & $>$5 \\
+    \hline\hline
+    0 & 1.0647 & 0.004 & 0.0008 & 0.0001 & 0.0001 & 0.0001 & 0.0007 \\
+    1 & 0.2215 & 0.0452 & 0.0086 & 0.0047 & 0.0014 & 0.0004 & 0.0006 \\
+    2 & 0.1781 & 0.0554 & 0.056 & 0.0156 & 0.0059 & 0.0022 & 0.0035 \\
+    3 & 0.1063 & 0.0232 & 0.0289 & 0.019 & 0.007 & 0.005 & 0.0046 \\
+    4 & 0.0591 & 0.023 & 0.0265 & 0.0242 & 0.0217 & 0.0127 & 0.0111 \\
+    5 & 0.0255 & 0.0077 & 0.0086 & 0.0093 & 0.0065 & 0.0048 & 0.0078 \\
+    $>$5 & 0.0178 & 0.0098 & 0.0094 & 0.0103 & 0.0109 & 0.0134 & 0.0224 \\
+    \hline\hline
+  \end{tabular} \\
+  \begin{tabular}{r} Gammas: 1.1055 \\ \end{tabular}  
+  \label{tab:production_pAl25}
+\end{centering}\end{tablehere}
+\vspace{0.15 cm}
+
+\begin{multicols}{2}
 \section{Conclusions}
+
+High energy protons were necessary to penetrate the Aluminum cube and consequentially bring visibility to the Bragg curve, characterized by the stopping power of protons in each media due to pathway ionization.
+The total energy deposited into the volumes curiously seems to decrease beyond the peak with respect to beam energy in figure \ref{fig:pEDep_Al5_MeV}; what occurs here is a complete transmission of proportionately many protons through the Aluminum cube, and a continued travel of the protons into the Helium chamber, seen by the demonstrative schematic (fig.~\ref{fig:schematic}).
+This phenomena reappears in the charge deposition landscape of protons at high energies (fig.~\ref{fig:pChargeDep_Al5_MeV}), where we observe a conspicuous gain at the world's edge, $z=115cm$; the protons must then tramsmit directly through the Helium chamber to the edge of the defined world where the fine $z$-bin collects the charge of the primary.
+
+Neutrons, which do not ionize their penetration pathways, do not behave with a Bragg curve but rather undergo elastic scattering and nuclear interactions.
+The resulting destructive recoil effect is shown by the development of a energy deposition bias in the Aluminum cube (figs.~\ref{fig:nEDep_Al5_eV}, \ref{fig:nEDep_Al5_keV}, \ref{fig:nEDep_Al5_MeV}).
+Relatively few high energy neutrons are also found to transmit directly through the cube, evidenced by the small shifts in charge deposiition (fig.~\ref{fig:nChargeDep_Al5_MeV}) due to obliterated electrons travelling but tens of microns.
 
@@
 \end{thebibliography}
+\end{multicols}
+\appendix
+\newpage
+\section{Energy deposition for Al side of 10, 25 cm}\label{app:EDep}
+
+\begin{multicols}{2}
+
+%% Proton EDep figures
+\begin{figurehere}
+\centering
+\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_pEDep_eV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per eV-range proton}}
+\label{fig:pEDep_Al10_eV}
+\end{figurehere}
+\begin{figurehere}
+\centering
+\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_pEDep_keV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per keV-range proton}}
+\label{fig:pEDep_Al10_keV}
+\end{figurehere}
+\begin{figurehere}
+\centering
+\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_pEDep_MeV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per MeV-range proton}}
+\label{fig:pEDep_Al10_MeV}
+\end{figurehere}
+
+%% Neutron EDep figures
+\begin{figurehere}
+\centering
+\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_nEDep_eV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per eV-range neutron}}
+\label{fig:nEDep_Al10_eV}
+\end{figurehere}
+\begin{figurehere}
+\centering
+\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_nEDep_keV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per keV-range neutron}}
+\label{fig:nEDep_Al10_keV}
+\end{figurehere}
+\begin{figurehere}
+\centering
+\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_nEDep_MeV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per MeV-range neutron}}
+\label{fig:nEDep_Al10_MeV}
+\end{figurehere}
+
+%% Proton EDep figures
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_pEDep_eV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per eV-range proton}}
+\label{fig:pEDep_Al25_eV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_pEDep_keV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per keV-range proton}}
+\label{fig:pEDep_Al25_keV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_pEDep_MeV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per MeV-range proton}}
+\label{fig:pEDep_Al25_MeV}
+\end{figurehere}
+\vspace{0.15 cm}
+
+%% Neutron EDep figures
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_nEDep_eV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per eV-range neutron}}
+\label{fig:nEDep_Al25_eV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_nEDep_keV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per keV-range neutron}}
+\label{fig:nEDep_Al25_keV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_nEDep_MeV.png}}
+\caption{\small \emph{Energy deposition landscape (MeV) per MeV-range neutron}}
+\label{fig:nEDep_Al25_MeV}
+\end{figurehere}
+\vspace{0.2 cm}
 
 \end{multicols}
+\newpage
+\section{Charge deposition for Al side of 10, 25 cm}\label{app:ChargeDep}
 
-\appendix
-\newpage
-\section{Energy deposition for Al side = 10, 25 cm}\label{app:EDep}
+\begin{multicols}{2}
 
-\newpage
-\section{Charge deposition for Al side = 10, 25 cm}\label{app:ChargeDep}
+%% Proton ChargeDep figures
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_pChargeDep_eV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per eV-range proton}}
+\label{fig:pChargeDep_Al10_eV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_pChargeDep_keV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per keV-range proton}}
+\label{fig:pChargeDep_Al10_keV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_pChargeDep_MeV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per MeV-range proton}}
+\label{fig:pChargeDep_Al10_MeV}
+\end{figurehere}
+\vspace{0.15 cm}
 
+%% Neutron ChargeDep figures
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_nChargeDep_eV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per eV-range neutron}}
+\label{fig:nChargeDep_Al10_eV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_nChargeDep_keV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per keV-range neutron}}
+\label{fig:nChargeDep_Al10_keV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{0.9\columnwidth}{!}{\includegraphics{pics/Al10/fig_nChargeDep_MeV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per MeV-range neutron}}
+\label{fig:nChargeDep_Al10_MeV}
+\end{figurehere}
+\vspace{0.15 cm}
+
+%% Proton ChargeDep figures
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_pChargeDep_eV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per eV-range proton}}
+\label{fig:pChargeDep_Al25_eV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_pChargeDep_keV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per keV-range proton}}
+\label{fig:pChargeDep_Al25_keV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_pChargeDep_MeV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per MeV-range proton}}
+\label{fig:pChargeDep_Al25_MeV}
+\end{figurehere}
+\vspace{0.15 cm}
+
+%% Neutron ChargeDep figures
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_nChargeDep_eV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per eV-range neutron}}
+\label{fig:nChargeDep_Al25_eV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_nChargeDep_keV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per keV-range neutron}}
+\label{fig:nChargeDep_Al25_keV}
+\end{figurehere}
+\vspace{0.15 cm}
+\begin{figurehere}
+\centering
+\resizebox{\columnwidth}{!}{\includegraphics{pics/Al25/fig_nChargeDep_MeV.png}}
+\caption{\small \emph{Charge displacement landscape (gain) per MeV-range neutron}}
+\label{fig:nChargeDep_Al25_MeV}
+\end{figurehere}
+\vspace{0.15 cm}
+
+\end{multicols}
 \end{document}

### 2015-03-15 bin/cube-to-cyl.cc

@@ -196,7 +196,7 @@ int main(int argc,char** argv) {
     G4String runGnuplot = "gnuplot graphs.gplot";
     system(runGnuplot);
 
-    // Remove state flag and Analysis/Events dirs
+    // Remove state flag
     G4String runRm = "rm " + data_dir + ".state";
     system(runRm);
   }

### 2015-03-15 bin/src/EventAction.cc

@@ -166,7 +166,7 @@ void EventAction::EndOfEventAction(const G4Event* event) {
     productionInFileStream.close();
   }
 
-  // Get normalized event production tallies continuously append to productionFileName
+  // Get normalized event production tallies continuously append matrixProtonsNeutrons
   eventFileNameStream.str(""); eventFileName = "";
   eventFileNameStream << data_dir << data_dir_geo << Al_side << "/" << data_dir_particle << data_dir_energy << E_Num << "/" << data_dir_analysis << "3/event" << eventNum << ".txt";
   eventFileName = eventFileNameStream.str();
@@ -186,9 +186,9 @@ void EventAction::EndOfEventAction(const G4Event* event) {
     }
     eventFileStream.close();
 
-    /*// Remove event file
+    // Remove event file
     runRm = "rm " + eventFileName;
-    system(runRm);*/
+    system(runRm);
   } else { 
     // Add zeroed count to matrix
     matrixProtonsNeutrons[0][0] += 1;

### 2015-03-15 bin/src/RunAction.cc

@@ -191,9 +191,6 @@ void RunAction::EndOfRunAction(const G4Run* run) {
       }
       productionInFileStream.close();
     }
-    // Remove Event files per run
-    runRmStream << "rm " << data_dir << data_dir_geo << Al_side << "/" << data_dir_particle << data_dir_energy << E_Num << "/" << data_dir_events << "/*";
-    runRm = runRmStream.str(); system(runRm);
     
     // Energies for label [future work: generalize arbitrary energy list]
     G4int E_Int = (E_Num % 5); if ( E_Int == 0 ) { E_Int = 5; }
@@ -270,7 +267,7 @@ void RunAction::EndOfRunAction(const G4Run* run) {
     system(runGnu);
 
     // Remove event files
-    //runRmStream << "rm " << data_dir << data_dir_geo << Al_side << "/" << data_dir_particle << data_dir_energy << E_Num << "/" << data_dir_events << "/*";
-    //runRm = runRmStream.str(); system(runRm);
+    runRmStream << "rm " << data_dir << data_dir_geo << Al_side << "/" << data_dir_particle << data_dir_energy << E_Num << "/" << data_dir_events << "/*";
+    runRm = runRmStream.str(); system(runRm);
   }
 }
